Fig1

### 2020-03-04 analysis/figure-1.Rmd
new fig 1

a <- plottsneelipse(chartsne, chartsne$tissue, allcolors) + labs(subtitle = "tissue\n")    
b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "tissue * sex\n")    
c <- plottsneelipse(ftsne, ftsne$treatment, allcolors ) + labs(y = " ", subtitle = "treatment * tissue\nfemales")
d <- plottsneelipse(mtsne, mtsne$treatment, allcolors ) + labs(y = " ", subtitle = "treatment * tissue\nmales")

@@

h <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + labs(subtitle = "hypothalamus")  + facet_wrap(~sex)
i <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + labs(subtitle = "pituitary", y = NULL) + facet_wrap(~sex) 
j <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + labs(subtitle = "gonads", y = NULL)  + facet_wrap(~sex)

@@

fig1 <- plot_grid(abcde, hij, nrow = 2, rel_heights = c(0.6,0.4))
fig1
```

>>>>

a <- plottsneelipse(chartsne, chartsne$tissue, allcolors) + labs(subtitle = "~ tissue")    
b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "~ tissue * sex")    
c <- plottsneelipse(ftsne, ftsne$tissue, allcolors ) + labs(y = " ", subtitle = "female ~ tissue")
d <- plottsneelipse(mtsne, mtsne$tissue, allcolors ) + labs(y = " ", subtitle = "male * tissue")

@@

h <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + labs(subtitle = "hypothalamus ~ treatment")  + facet_wrap(~sex, scales = "free")
i <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + labs(subtitle = "pituitary ~ treatment", y = NULL) + facet_wrap(~sex, scales = "free") + theme(legend.position = )
j <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + labs(subtitle = "gonads ~ treatment", y = NULL)  + facet_wrap(~sex, scales = "free")

@@

fig1 <- plot_grid(abcde, hij, nrow = 2, rel_heights = c(0.6,0.4))
fig1
